\documentclass[12pt]{article}
\usepackage{fullpage,url}\setlength{\parskip}{3mm}\setlength{\parindent}{0mm}
\begin{document}

\begin{center}\bf
Homework 4. Due by 5pm on Wednesday 9/30.

Research misconduct
\end{center}
Read pages 15--23 of {\em On Being a Scientist}. We're going to focus on some gray areas in plagiarism. Read Pachter's blog posting at 
\url{liorpachter.wordpress.com/2014/09/12}.
Write brief answers to the following questions, by editing the tex file at \url{dept.stat.lsa.umich.edu/~ionides/810/hw04.tex}, and send me the resulting pdf file. 

\begin{enumerate}

\item Self-plagiarism is a subtle topic. Do you think the authors (RNSD) did anything wrong? What, if anything, should be done to correct the situation? 

YOUR ANSWER HERE.

\item Comment on any details of the case that help you to make up your mind about it.

YOUR ANSWER HERE.

\item If you look, you will find common academic practices that are uncomfortably close to plagiarism. For example,

(i) Homework and exam problems may be copied or adapted from a textbook, without attribution.

(ii) Figures taken from papers and other internet sources may be presented in talks and courses without attribution.

Should a responsible researcher attempt to avoid these RCRS gray areas? How? What are the advantages and disadvantages of following RCRS practices that are not currently universally adopted?

YOUR ANSWER HERE.

\item Are there any forms of inappropriate scientific conduct that you think have the combination of severity and prevalence to threaten the proper functioning of modern science? Are you more concerned about the total effect of serious (and presumably rare) misconduct, or milder (and potentially more common) misconduct?

YOUR ANSWER HERE.

\end{enumerate}
\end{document}
